Considering scale in multilayer animal social networks

### 2020-06-21 paper/manuscript.Rmd
order edge overlap, str, etc

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social distance threshold. For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open). Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Open and foraging layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.

<!-- Figure: metrics by land cover resolution -->
(ref:lcres) Varying spatial scale of land cover raster. For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open). A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m). D) Edge overlap of habitat layers across spatial resolutions. Open and forest layers show consistent edge overlap with increasing spatial resolution while foraging shows a sharp decline in edge overlap between 30 m and 600 m. Above 600 m, the foraging layers are stable. E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution. Foraging layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution. Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open). A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations. B) Edge overlap increased for all habitat layers with increasing number of observations. Open and foraging layers had higher edge overlap than forest layers. C) Multidegree increased for all individuals with increasing number of observations. Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).

@@

<!-- JWT: edge overlap, graph strength, and multidegree are presented in different orders in the graphs. They should be presented in the same order each time even if the combination of what you show changes. -->

@@

(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut != 1, format(min(mindate), '%F')]` and `r DT[, format(max(datetime), '%F')]`. Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed. Twelve layers represent combinations of four time windows and three habitat classes (open, forest and foraging). Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).

>>>>

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social distance threshold. For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open). Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Foraging and open layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.

<!-- Figure: metrics by land cover resolution -->
(ref:lcres) Varying spatial scale of land cover raster. For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open). A) Edge overlap of habitat layers across spatial resolutions. Open and forest layers show consistent edge overlap with increasing spatial resolution while foraging shows a sharp decline in edge overlap between 30 m and 600 m. Above 600 m, the foraging layers are stable. B) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution. Foraging layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution. Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest. C, D, E) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open). A) Edge overlap increased for all habitat layers with increasing number of observations. Foraging and open layers had higher edge overlap than forest layers. B) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations. C) Multidegree increased for all individuals with increasing number of observations. Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).

@@

@@

(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut != 1, format(min(mindate), '%F')]` and `r DT[, format(max(datetime), '%F')]`. Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed. Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest and open). Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).
